Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-14 paper/paper.tex
pass on intro

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the official
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}.\Comment{ This test suite contains
  87\% of all the tests we used.} We also considered test suites of
three of the four engines mentioned in
Section~\ref{sec:methodology:engines} and four other engines. Overall,
we selected a total of \totfiles{} JS
files. Table~\ref{tab:test-suites} shows the breakdown of tests we
considered. Column ``original'' shows the number of test cases for
each test suite. We did not consider tests from the \chakra{}
repository because they depend on non-portable objects. Notice that
the number of tests in \veight\ is low. That happens because \veight{}
uses many tests from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. The columns
``compile-in-all'' and ``no-fail-in-all'' indicate the tests used in
the test transplantation experiment and the differential testing
experiment, respectively.

Column ``pass-in-par.'' shows the number of test cases that pass in
their parent engine. We discarded tests that fail in their parent
engine as we could not reliably indicate the reason for the failure,
so we assumed the test could be broken. We removed 63 test cases that
fail for that reason--6 tests from \jsc{} and 57 tests from
\smonkey. Column ``compile-in-all'' shows the number of test cases
whose executions do not throw errors because of an undefined variable
or property. We capture these cases by looking for the presence of
\CodeIn{ReferenceError} and \CodeIn{TypeError} in the output. A
\CodeIn{ReferenceError} (respectively, \CodeIn{TypeError}) is raised
when test execution attempts to access an undefined variable
(respectively, property of an object). We discarded those tests to
avoid noise in the experiments as they clearly indicate some missing
feature as opposed to bugs. For example, some tests use non-portable
names (\eg{}, \jsc{}'s \CodeIn{drainMicrotasks()} and \smonkey{}'s
\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
spec, not all engines currently support. We used the
\totalTestFilesForTestTransplantation{} tests included in the circle
from the table in the evaluation of test transplantation, \ie{}, the
difference between sets ``compile-in-all'' and Test262. We did not
consider tests from the conformance suite as they are more likely to
indicate missing features as opposed to bugs. In addition, engine
developers have access to these test and are encouraged to run
them. Column ``no-fail-in-all'' shows the tests for which all engines
pass. This test set is used in the evaluation of differential
testing. Note that it is a proper subset of the ``compile-in-all''
test set. The tests from this group are used as fuzzing seeds. The
guarantee that they pass in all engines assures that, if discrepancies
occur, they are related to the changes in the input as opposed to the
original cause of failure.

It is also worth mentioning that some engines use a custom shell to
run tests, including a harness with specific assertions.  For that, we
needed to make minor changes in the testing infrastructure to be able
to run the tests uniformly across all engines. More precisely, we
needed to mock non-portable harness functions, which are only
available to certain engines.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test cases per
    suite. Column ``original'' shows the original size of the test
    suite, column ``compile-in-all'' shows the number of test cases
    for which engines do not throw compile error (\eg{}, undefined
    name), and column ``no-fail-all'' shows the number of test cases
    that pass in all four engines we analyzed.}
  \setlength{\tabcolsep}{2.25pt}      
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & original & pass-in-par. & compile-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & 31,276 & - &  29,846 & 17,639 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 & 1,025 &\marktopleft{c1}1,021 & 955\\
    \smonkey\ & \cite{mozilla} & 2,634 & 1,977 & 2,116 & 1,686\\
    \veight{} & \cite{v8} & 75 & 75 & 57 & 57\\
    \midrule
    Duktape & \cite{duktape} & 1,195 & 1,195 & 921 & 915\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,951 & 1,878 & 1,837\\
    JSI & \cite{jsi} & 99 & 99 & 63 & 63\\
    Tiny-js & \cite{tinyjs} & 49 & 49 & 37\markbottomright{c1} & 37\\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule 
  \end{tabular}
\end{table}

For example to run the \jerry{} tests it was necessary 
use the unit-test package to run it, but with our changes we added the assertion
does not have an assertion in the test file
\Fix{add code to explain}

>>>>

\subsection{Seed JS files\label{sec:seeds}}~
A good test set is critical for finding bugs with the techniques used
in this paper. For that reason, we looked for \js\ files from various
sources: 1) test files from the Test262~\cite{tc39-github} conformance
suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
from the test suite of the selected engines (see
Section~\ref{sec:methodology:engines}); these files are accessible
from the engine's official repositories, 3) test files mined from
issue trackers of these engines, and 4) test files from public engines
accessible from GitHub using the GitHub REST
API~\cite{github-rest-api}.

Table~\ref{tab:test-suites} shows the breakdown of tests we per
source. Column ``original'' shows the number of test cases associated
with each test suite. Column ``pass-in-par.'' shows the number of test
cases that pass in their parent engine. We discarded tests that fail
in their parent engine as we could not reliably indicate the reason
for the failure, so we assumed the test could be broken. We removed 63
test cases that fail for that reason--6 tests from \jsc{} and 57 tests
from \smonkey. Column ``compile-in-all'' shows the number of test
cases whose executions do not throw dynamic type errors in any of the
engines because of an undefined variable or property. We capture these
cases by looking for the presence of \CodeIn{ReferenceError} and
\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc{}'s
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. We used the \totalTestFilesForTestTransplantation{}
tests included in the circle from the table in the evaluation of test
transplantation, \ie{}, all tests under the ``compile-in-all''
column\Mar{change name to type-in-all}
but the Test262 tests. We did not consider tests from the conformance
suite as they are more likely to indicate missing features as opposed
to bugs. In addition, engine developers have access to these test and
are encouraged to run them.  Column ``no-fail-in-all'' shows the tests
for which all engines pass. This test set is used in the evaluation of
differential testing. Note that it is a proper subset of the
``compile-in-all'' test set. The tests from this group are used as
fuzzing seeds. The guarantee that they pass in all engines assures
that, if discrepancies occur, they are related to the changes in the
input as opposed to the original cause of failure.

%% The main source of test
%% cases is the official Test262~\cite{tc39-github} conformance test
%% suite for the ECMA262 specification~\cite{ecmas262-spec}.\Comment{
%%   This test suite contains 87\% of all the tests we used.} We also
%% considered test suites of three of the four engines mentioned in
%% Section~\ref{sec:methodology:engines} and four other engines. Overall,
%% we selected a total of \totfiles{} JS
%% files.

\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
depend on external libraries, which not all selected engines
support. We decided to discard those. For example, many tests we found
required a Node.js runtime~\cite{node} for execution. Also, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects. Finally, note that the number of tests in
\veight\ is low; that happens because \veight{} uses many tests from
Mozilla and \jsc{}; we discarded those to avoid repetition and to give
credit where it is due. \lbrack{}Test Harness\rbrack{}~It is also
worth mentioning that some engines use a custom shell to run tests,
including a harness with specific assertions.  For that, we needed to
make minor changes in the testing infrastructure to be able to run the
tests uniformly across all engines. More precisely, we needed to mock
non-portable harness functions, which are only available in certain
engines.

\subsubsection{Mining Tests from Issue Trackers}

\Fix{...elaborate...}

\Mar{-------- estou aqui}

%% \Fix{revise this}
%% For example to run the \jerry{} tests it was necessary 
%% use the unit-test package to run it, but with our changes we added the assertion
%% does not have an assertion in the test file
%% \Fix{add code to explain}

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test cases per
    suite. Column ``original'' shows the original size of the test
    suite, column ``compile-in-all'' shows the number of test cases
    for which engines do not throw compile error (\eg{}, undefined
    name), and column ``no-fail-all'' shows the number of test cases
    that pass in all four engines we analyzed.\Mar{explain
      ``pass-in-par.''}\Mar{why SpiderMonkey 1,977->2,116?}}
  \setlength{\tabcolsep}{2.25pt}      
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & original & pass-in-par. & compile-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & 31,276 & - &  29,846 & 17,639 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 & 1,025 &\marktopleft{c1}1,021 & 955\\
    \smonkey\ & \cite{mozilla} & 2,634 & 1,977 & 2,116 & 1,686\\
    \veight{} & \cite{v8} & 75 & 75 & 57 & 57\\
    \midrule
    Duktape & \cite{duktape} & 1,195 & 1,195 & 921 & 915\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,951 & 1,878 & 1,837\\
    JSI & \cite{jsi} & 99 & 99 & 63 & 63\\
    Tiny-js & \cite{tinyjs} & 49 & 49 & 37\markbottomright{c1} & 37\\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule 
  \end{tabular}
\end{table}
